Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-07-17 surfaces-write-up/surface-write-up.tex
fix ref

By ~\ref{lem:bound-ker-chi}, $\ker(\chi)$ is generated in degrees 
up to $2\sum_{i=1}^n \ell_i a_i$ and by Lemma ~\ref{lem:proj-
relations-psi}, $\ker(\psi),$ is generated in degrees up to $\frac{
\bida_i}{\deg(D)} + \sum_{i=1}^n \ell_i a_i.$ Consequently, Lemma ~
\ref{lem:composite-map} implies that $\ker(\phi)$ is generated in 
degrees less than
\[
	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}
	(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
\]
\end{proof}

>>>>

By ~\ref{lem:bound-ker-chi}, $\ker(\chi)$ is generated in degrees 
up to $2\sum_{i=1}^n \ell_i a_i$ and by Lemma
~\ref{lem:proj-relations-psi}, $\ker(\psi),$ is generated in
degrees up to $\frac{\bida_i}{\deg(D)} + \sum_{i=1}^n \ell_i a_i$. 
Consequently, Lemma ~\ref{lem:composite-map} implies that $\ker(\phi)$
is generated in degrees less than
\[
	\max \left(2 \sum_{i=1}^n \ell_i a_i, \frac{\max_{1\le i \le n}
	(\bida_i)}{\deg(D)} + \sum_{i=1}^n \ell_i a_i \right).
\]
\end{proof}
